Title Goes Here

### 2020-04-04 analysis/paper/paper.Rmd
Work with Ben

Here is a citation [@Marwick2017]

@@

@@

Computing Coefficient or variation
```{r}
# Coefficient of variation (CV)
library(goeveg)
CV_ML <- cv(ML, na.rm = FALSE) #na.rm: logical. Should missing values be removed?
CV_BL <- cv(BL, na.rm = FALSE)
CV_TL <- cv(TL, na.rm = FALSE)
CV_SL <- cv(SL, na.rm = FALSE)
CV_MW <- cv(MW, na.rm = FALSE)
CV_TW <- cv(TW, na.rm = FALSE)
CV_SW <- cv(SW, na.rm = FALSE)

#simpler way to calculate CV (%)
sd(ML)/mean(ML)*100
sd(BL)/mean(BL)*100
sd(TL)/mean(TL)*100
sd(SL)/mean(SL)*100
sd(MW)/mean(MW)*100
sd(TW)/mean(TW)*100
sd(SW)/mean(SW)*100

@@

PCA <- prcomp(DF, center = TRUE,scale. = TRUE)

#group them by three phase
library(ggfortify) 
autoplot(prcomp(DF), data = df_sitename, colour = as.factor(df_sitename$SPstage.Stage))

@@

#read all files from raw_data

lm_landmarks <- readalltps(here("analysis/data/raw_data"))

>>>>

- What are our research questions?

- What is our archaeological background?

- What is our conceptual framework?

- What are our methods?

- What are our results?

- What is the answer to our questions??

@@

Make a table of the CV for all variables on all artefacts from all sites

```{r}
# all artefacts from all sites
map_df(DF, cv)
```

Make a table of CVs for all variable grouped by site

```{r}
cv_by_site_df  <- 
df_sitename %>% 
  select(-SPstage.Stage) %>% 
  group_by(sitename) %>% 
  add_tally() %>% 
  filter( n > 1) %>% 
  select(-n) %>% 
  nest(-sitename) %>% 
  mutate(cv_by_site = map(data, ~map_df(.x, cv)))

cv_by_site_df_unnest <-   
cv_by_site_df %>% 
  unnest(cv_by_site)
```

Make a table of CVs for all variable grouped by phase
```{r}
cv_by_stage_df  <- 
df_sitename %>% 
  select(-sitename) %>% 
  group_by(SPstage.Stage) %>% 
  add_tally() %>% 
  filter( n > 1) %>% 
  select(-n) %>% 
  nest(-SPstage.Stage) %>% 
  mutate(cv_by_stage = map(data, ~map_df(.x, cv)))

cv_by_stage_df_unnest <-   
cv_by_stage_df %>% 
  unnest(cv_by_stage)
```

@@

Computing Coefficient or variation
```{r}
# Coefficient of variation (CV)

cv <- function(x, ... ) sd(x, ...) / mean(x, ...) *100

# we've got DF a data frame with cols as variables
# rows and specimens, and values as dimensions
# need to add a column of site ID
map(DF, cv)

CV_ML <- cv(ML, na.rm = FALSE) #na.rm: logical. Should missing values be removed?
CV_BL <- cv(BL, na.rm = FALSE)
CV_TL <- cv(TL, na.rm = FALSE)
CV_SL <- cv(SL, na.rm = FALSE)
CV_MW <- cv(MW, na.rm = FALSE)
CV_TW <- cv(TW, na.rm = FALSE)
CV_SW <- cv(SW, na.rm = FALSE)

sd(DF$ML)/mean(DF$ML)*100
sd(BL)/mean(BL)*100
sd(TL)/mean(TL)*100
sd(SL)/mean(SL)*100
sd(MW)/mean(MW)*100
sd(TW)/mean(TW)*100
sd(SW)/mean(SW)*100

@@

PCA <- prcomp(DF, center = TRUE, scale = TRUE)

#group them by three phase
library(ggfortify) 
ap <- 
autoplot(prcomp(DF, center = TRUE, scale = TRUE), 
         data = df_sitename, 
         colour = as.factor(df_sitename$SPstage.Stage))

pca_col <- data.frame(PCA$x, phase = as.factor(df_sitename$SPstage.Stage))

gg <- 
ggplot(pca_col ,
       aes(PC1,
           PC2,
       colour = phase)) +
  geom_point()

gg

# remove stage 1 artefact
xx_pca <- 
df_sitename %>% 
  filter(SPstage.Stage != 1) %>% 
  select(-sitename) %>% 
  prcomp(., center = TRUE, scale = TRUE)

xx_pca1 <- data.frame(xx_pca$x,stage = as.factor( df_sitename$SPstage.Stage[df_sitename$SPstage.Stage !=1]))

gg_stage <- 
ggplot(xx_pca1 ,
       aes(PC1,
           PC2,
       colour = stage)) +
  geom_point() +
  stat_ellipse()

gg_stage
```

We see some differences in artefact shape and size. Now we need to examins the PCA output numbers to describe in more details.

@@

#read all files from raw_data
tps_files <- list.files(here("analysis/data/raw_data"), full.names = TRUE)
lm_landmarks <- map(tps_files, readalltps)
names(lm_landmarks) <- list.files(here("analysis/data/raw_data"))
